Fourmile Calibrations and Output

### 2025-05-06 params.Rmd
changed order of param boxplots to match order of processes
reorder burn/unburn params to match order of processes

@@

@@

ggsave('./figures/burn_unburn_params_tukey_pts.png',
       dpi=600,
       width = 12,
       height = 8)

>>>>

param_sens$param <- factor(param_sens$param, levels = c("snow_trs", 
                                                        "baseTemp", 
                                                        "t_factor",
                                                        "a_rain",
                                                        "a_snow",
                                                        "lagSurfaceRunoff",
                                                        "soilLatVertLPS",
                                                        "soilOutLPS",
                                                        "lagInterflow"))

@@

# reorder the params
combo$param <- factor(combo$param, levels = c("a_snow",
                                                        "a_rain",
                                                        "soilMaxInfSummer",
                                                        "soilMaxDPS",
                                                        "lagSurfaceRunoff",
                                                        "soilDistMPSLPS"))

@@

ggsave('./figures/burn_unburn_params_tukey_pts_reoder.png',
       dpi=600,
       width = 12,
       height = 8)
